Additional analysis

### 2018-04-30 03_additional-analysis.Rmd
Minor changes from upgrading to R 3.5

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(ggridges)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(here)

@@

```{r avg-time, results="asis"}
results %>% 
  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
  gather(Statistic, value) %>% 
  mutate(value = seconds_to_period(value)) %>% 
  mutate(Minutes = sprintf("%02d:%02d", minute(value), second(value))) %>% 
  select(-value) %>% 
  pandoc.table()
```

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Unload all the already-loaded packages because R Markdown websites *don't* knit 
# each Rmd in a separate environment: https://github.com/rstudio/rmarkdown/issues/1326
#
# This means that here::here() and lubridate::here() will conflict becuase **here**
# has already been loaded in previous scripts
if (isTRUE(getOption('knitr.in.progress')) & !is.null(names(sessionInfo()$otherPkgs))) {
  invisible(suppressWarnings(sapply(paste0("package:", names(sessionInfo()$otherPkgs)),
                                    detach, character.only = TRUE)))
}

# Load libraries again
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(ggridges)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(here)

@@

```{r avg-time, results="asis"}
results %>% 
  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
  gather(Statistic, value) %>% 
  mutate(value = seconds_to_period(value)) %>% 
  mutate(Minutes = sprintf("%02.0f:%02.0f", minute(value), second(value))) %>% 
  select(-value) %>% 
  pandoc.table()
```
